Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells. For a Hele-Shaw cell of a given size, flow development depends only on the capillary number $\left(\text{N}_{c}\right)$, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959} \citep[see also][]{homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.

>>>>

More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells. For a Hele-Shaw cell of a given size, flow development depends only on the capillary number $\left(\text{N}_{c}\right)$, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959b} \citep[see also][]{saffman_1959,homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.
